Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2012-04-03 article.tex
Added reference for TaylorF2
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1492 ccdd05d5-56c1-461a-bf98-85f6876523b4
Added department affiliation
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1493 ccdd05d5-56c1-461a-bf98-85f6876523b4

\altaffiltext{1}{Canadian Institute for Theoretical Astrophysics, Toronto, ON, Canada}
\altaffiltext{2}{D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, Cachan, France}
\altaffiltext{3}{LIGO Laboratory, California Institute of Technology, MC 100-36, 1200 E. California Blvd., Pasadena, CA, USA; \texttt{leo.singer@ligo.org}}
\altaffiltext{4}{Facultat de F\'{i}sica, Universitat de Val\`{e}ncia, Burjassot, Spain} 
\altaffiltext{5}{University of Texas at Austin, Austin, TX, USA}
\altaffiltext{6}{Center for Computational Relativity and Gravitation and School of Mathematical Sciences, Rochester Institute of Technology, Rochester, NY, USA}
\altaffiltext{7}{Perimeter Institute for Theoretical Physics, Waterloo, ON, Canada}
\altaffiltext{8}{Department of Physics and Astronomy, Barnard College, Columbia University, New York, NY, USA}
\altaffiltext{9}{Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r Gravitationphysik, Hannover, Germany}
\altaffiltext{10}{Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\altaffiltext{11}{Ryerson University, Toronto, ON, Canada}

@@

We examine the performance of the \lloid\ algorithm on a small region of
compact binary parameter space centered on typical \NS--\NS\
masses.  We begin by constructing a template bank that spans component masses
from 1~to~3~$M_\odot$ using a simulated Advanced \LIGO\ noise
power spectrum~\citep{ALIGONoise}\footnote{\url{http://dcc.ligo.org/cgi-bin/DocDB/ShowDocument?docid=T0900288&version=3}}.  Templates are truncated at 10~Hz, where the projected
sensitivity of Advanced \LIGO\ is interrupted by the ``seismic wall.''
This results in a grid of 98544 points, or
$2 \times 98544 = 197088$~templates.  Then we create sub-banks by partitioning
the parameter space by chirp mass.  Figure \ref{fig:tmpltbank} illustrates this
procedure. We concentrate on a sub-bank with 657 points with chirp masses
between 1.1955 and 1.2045~$M_\odot$, or $2 \times 657 = 1314$~templates.
\begin{figure}[h]
	\plotone{f4}
	\caption{\label{fig:tmpltbank}Source parameters selected for sub-bank used in this
case study, consisting of component masses $m_1$, $m_2$, between 1 and 3~$M_\odot$, and
chirp masses $\mathcal{M}$ between 1.1955 and 1.2045~$M_\odot$.}
\end{figure}
With this sub-bank we are able to construct an efficient time-slice decomposition
that consists of 11 time slices with sample rates between 32 and 4096 Hz summarized
in Table~\ref{tab:time_slices}.
\begin{table*}
\caption{\label{tab:time_slices} Filter design sub-bank of 1314 templates.  From
left to right, this table shows the sample rate, time interval, number of
samples, and number of orthogonal templates for each time slice.  We vary \SVD\
tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\begin{center}
\begin{minipage}[c]{0.4\textwidth}
\includegraphics{t3}
\end{minipage}
\begin{minipage}[c]{0.55\textwidth}
\begin{tabular}{rr@{,\,}lc*{6}{r}}
\tableline\tableline
\\ [-2ex]
$f^s$ & $[t^s$&$t^{s+1})$ & &\multicolumn{6}{c}{$-\log_{10}$ (1$-$\SVD\ tolerance)} \\% [1ex]
\cline{5-10}
\\[-2.5ex]
(Hz) & \multicolumn{2}{c}{(s)} & $N^s$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ \\ \tableline
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\tableline
\end{tabular}
\end{minipage}
\end{center}
\end{table*}
We use this sub-bank and decomposition for the remainder of this section.

>>>>

\altaffiltext{1}{Canadian Institute for Theoretical Astrophysics, Toronto, ON, Canada}
\altaffiltext{2}{D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, Cachan, France}
\altaffiltext{3}{LIGO Laboratory, California Institute of Technology, MC 100-36, 1200 E. California Blvd., Pasadena, CA, USA; \texttt{leo.singer@ligo.org}}
\altaffiltext{4}{Facultat de F\'{i}sica, Universitat de Val\`{e}ncia, Burjassot, Spain} 
\altaffiltext{5}{Department of Physics, University of Texas at Austin, Austin, TX, USA}
\altaffiltext{6}{Center for Computational Relativity and Gravitation and School of Mathematical Sciences, Rochester Institute of Technology, Rochester, NY, USA}
\altaffiltext{7}{Perimeter Institute for Theoretical Physics, Waterloo, ON, Canada}
\altaffiltext{8}{Department of Physics and Astronomy, Barnard College, Columbia University, New York, NY, USA}
\altaffiltext{9}{Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r Gravitationphysik, Hannover, Germany}
\altaffiltext{10}{Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\altaffiltext{11}{Ryerson University, Toronto, ON, Canada}

@@

We examine the performance of the \lloid\ algorithm on a small region of
compact binary parameter space centered on typical \NS--\NS\
masses.  We begin by constructing a template bank that spans component masses
from 1~to~3~$M_\odot$ using a simulated Advanced \LIGO\ noise
power spectrum~\citep{ALIGONoise}\footnote{\url{http://dcc.ligo.org/cgi-bin/DocDB/ShowDocument?docid=T0900288&version=3}}.  Waveforms are generated in the frequency domain in the stationary phase approximation at (post)$^{3.5}$-Newtonian order in phase and Newtonian order in amplitude \citep[the TaylorF2 waveforms described in][]{TaylorF2}.  Templates are truncated at 10~Hz, where the projected
sensitivity of Advanced \LIGO\ is interrupted by the ``seismic wall.''
This results in a grid of 98544 points, or
$2 \times 98544 = 197088$~templates.  Then we create sub-banks by partitioning
the parameter space by chirp mass.  Figure \ref{fig:tmpltbank} illustrates this
procedure. We concentrate on a sub-bank with 657 points with chirp masses
between 1.1955 and 1.2045~$M_\odot$, or $2 \times 657 = 1314$~templates.
\begin{figure}[h]
	\plotone{f4}
	\caption{\label{fig:tmpltbank}Source parameters selected for sub-bank used in this
case study, consisting of component masses $m_1$, $m_2$, between 1 and 3~$M_\odot$, and
chirp masses $\mathcal{M}$ between 1.1955 and 1.2045~$M_\odot$.}
\end{figure}
With this sub-bank we are able to construct an efficient time-slice decomposition
that consists of 11 time slices with sample rates between 32 and 4096 Hz summarized
in Table~\ref{tab:time_slices}.
\begin{table*}
\caption{\label{tab:time_slices} Filter design sub-bank of 1314 templates.  From
left to right, this table shows the sample rate, time interval, number of
samples, and number of orthogonal templates for each time slice.  We vary \SVD\
tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\begin{center}
\begin{minipage}[c]{0.4\textwidth}
\includegraphics{t3}
\end{minipage}
\begin{minipage}[c]{0.55\textwidth}
\begin{tabular}{rr@{,\,}lc*{6}{r}}
\tableline\tableline
\\ [-2ex]
$f^s$ & $[t^s$&$t^{s+1})$ & &\multicolumn{6}{c}{$-\log_{10}$ (1$-$\SVD\ tolerance)} \\% [1ex]
\cline{5-10}
\\[-2.5ex]
(Hz) & \multicolumn{2}{c}{(s)} & $N^s$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ \\ \tableline
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\tableline
\end{tabular}
\end{minipage}
\end{center}
\end{table*}
We use this sub-bank and decomposition for the remainder of this section.
